Supplementary figures

### 2021-07-20 code/figure6.Rmd
Edit manuscript based on editor comments

	## Plotting
	ggplot(dfclas,aes_(x = quote(value),y = quote(class), fill = quote(class))) + geom_density_ridges(alpha = alpha.setup) +
		facet_wrap(. ~ facetname,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
	  theme(legend.position = "none") + ggtitle("Class Specific Coefficients") +
	  labs(x = expression(paste("A"["cl"])), y = "Cluster Identity") +
	  theme(plot.title= element_text(hjust = 0.5)) +
	  scale_fill_manual(values = cluster.colours) +
	  scale_x_continuous(breaks=seq(0.5,1.5, by = 0.5), limits = c(0.5,1.5)) +
    geom_vline(aes(xintercept=1), linetype = "dashed", color = "red")
```

>>>>

	## Plotting
	ggplot(dfclas,aes_(x = quote(value),y = quote(class), fill = quote(class))) + geom_density_ridges(alpha = alpha.setup) +
		facet_wrap(. ~ facetname,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
	  theme(legend.position = "none") +
	  labs(x = expression(paste("A"["cl"])), y = "Cluster Identity") +
	  theme(plot.title= element_text(hjust = 0.5)) +
	  scale_fill_manual(values = cluster.colours) +
	  scale_x_continuous(breaks=seq(0.5,1.5, by = 0.5), limits = c(0.5,1.5)) +
    geom_vline(aes(xintercept=1), linetype = "dashed", color = "red")
```

### 2021-07-20 code/supplemental_v2.Rmd
Edit manuscript based on editor comments

---
title: "Supplementary figures"
output:
  word_document:
    reference_docx: "../text/word-style-reference-ttmanu-iscb-iscience-v2.docx"
always_allow_html: TRUE
editor_options:
  chunk_output_type: console
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=600, warning = FALSE, message = FALSE)
suppressPackageStartupMessages(c(
  library(tidyverse),
  library(data.table),
  library(plot3D),
  library(flextable),
  library(knitr),
  library(kableExtra),
  library(xlsx),
  library(patchwork)
))
```

@@

**Figure S1. Distribution of cancer type on UMAP clusters.** Each panel shows the identity of 
individual tumors by one of 23 cancer types projected onto the cluster UMAP identified 
in **Figure 1B of the main text**. The colors indicate the tumor's cluster identity.

@@

**Figure S2. Histological subtypes.** Each panel shows the histological subtypes of one of the 23 
cancers projected onto the tumors of the UMAP from **Figure 1B of the main text**. The colors indicate the tumor's histological subtype identity.

@@

**Figure S3. Distribution of mismatch repair genes on UMAP clusters.** Each panel shows one of 15 
genes involved in genome stability projected on the UMAP from **Figure 1B of the main text**. The colors indicate the tumor's cluster identity.

@@

**Figure S4. Distribution of oncogenes/tumor suppressors on UMAP clusters.** Each panel shows shows one of the twelve oncogenes/tumor suppressors projected onto the tumors of the UMAP from **Figure 1B of the main text**. The colors indicate the tumor's cluster identity.

@@

**Figure S5. Performance comparison of different classification model - knn, COCA, iCluster, tissue-of-origin (tis).** A) Empirical cumulative distribution function comparing time of death prediction of all classification models with actual time of death (dark green). B) Error distribution plot of predicted and actual time of death.

>>>>

---
output:
  word_document:
    reference_docx: "../text/word-style-reference-ttmanu-iscb-iscience-v2.docx"
always_allow_html: TRUE
editor_options:
  chunk_output_type: console
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=600, warning = FALSE, message = FALSE)
suppressPackageStartupMessages(c(
  library(tidyverse),
  library(data.table),
  library(plot3D),
  library(flextable),
  library(knitr),
  library(kableExtra),
  library(xlsx),
  library(patchwork)
))
```

@@

**Figure S1. Distribution of cancer type on UMAP clusters, Related to Figure 2.** Each panel shows the identity of 
individual tumors by one of 23 cancer types projected onto the cluster UMAP identified 
in **Figure 1B of the main text**. The colors indicate the tumor's cluster identity.

@@

**Figure S2. Histological subtypes, Related to Figure 2.** Each panel shows the histological subtypes of one of the 23 
cancers projected onto the tumors of the UMAP from **Figure 1B of the main text**. The colors indicate the tumor's histological subtype identity.

@@

**Figure S3. Distribution of mismatch repair genes on UMAP clusters, Related to Figure 2.** Each panel shows one of 15 
genes involved in genome stability projected on the UMAP from **Figure 1B of the main text**. The colors indicate the tumor's cluster identity.

@@

**Figure S4. Distribution of oncogenes/tumor suppressors on UMAP clusters, Related to Figure 2.** Each panel shows shows one of the twelve oncogenes/tumor suppressors projected onto the tumors of the UMAP from **Figure 1B of the main text**. The colors indicate the tumor's cluster identity.

@@

**Figure S5. Performance comparison of different classification model - knn, COCA, iCluster, tissue-of-origin (tis), Related to Figure 5.** A) Empirical cumulative distribution function comparing time of death prediction of all classification models with actual time of death (dark green). B) Error distribution plot of predicted and actual time of death.

```{r child='../code/figureSM1.Rmd'}
```

**Figure S6. Method for tumor classification using pathway aberration data, Related to Figure 1.** 
A) MCA analysis was performed to determine the eigenvalue with the most
explanatory power from the categorical data. Average of 100 permutations of the
data was used as a baseline. B) The p-value of each eigenvalue was plotted and
the max eigenvalue with a pvalue < 0.05 was selected. C) The resulting MCA was
projected down to 3 dimensions for the purpose of density based clustering (only
the first 2 dimensions are shown). Each dot represents a tumor D) HDBSCAN was
used to perform hierarchical density based clustering tuned to minimize the
fraction of unassigned tumors. E) HDBSCAN clustered tumors were visualized on
the UMAP projection; tumors are colored by cluster membership (see legend). This
results in some tumors remaining unclassified (grey points). F) kNN was used to
assign membership to the remaining tumors.

```{r child='../code/figureSM2.Rmd'}
```

**Figure S7. Comparison between CDC data and ODE model fit for
males and females of European descent, Related to Figure 5.** This comparison does not distinguish on
ethnicity for simplicity in visualization.

```{r sm3, fig.height=3, fig.width=6}
sm3.1 <- ggplot(data.frame(x=0:110),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,30.0,29.0/65),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(30, 110), breaks = c(seq(30,110, by =10))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for A"["0"])), y = "Probability Density")

sm3.2 <- ggplot(data.frame(x=0:3),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,50.0,49.0/1.0),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 1.6), breaks = c(seq(0.6, 1.5, by = 0.2))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for A"["cl"])), y = "Probability Density")

sm3.1 + sm3.2 + plot_annotation(tag_levels = "A") + plot_layout(design = layout)
```

**Figure S8. Priors for the tissue and class coefficients, Related to Figure 5 and 6.** A) The tissue
coefficient is chosen to admit ages between 40 and 100 years old as a baseline
age. B) Within a given tissue, the class parameter multiplies the tissue value and
is given a peak density at 1, and a credible range from near 0.6 to 1.4,
reflecting our expectation of a moderate multiplicative perturbation of
variation across the classes.

### 2021-07-20 code/survival/figure5.Rmd
Edit manuscript based on editor comments

  ## Simulation of women no cancer
  survyrswfref = sapply(agesw,function(a) tryCatch(simdeath(r20wf,ageratewf,a,1)/365,error= function(e) {0}))
  ## Effective age due to cancer
  effage.agesw <- effage0tiss * effage0 + effagert * (agesw - 20)
  survyrswf = sapply(effage.agesw,function(a) tryCatch(simdeath(r20wf,ageratewf,a,kmean)/365,error= function(e) {0}))

>>>>

  ## Simulation of women no cancer
  survyrswfref = sapply(agesw,function(a) tryCatch(simdeath(r20wf,ageratewf,a,1)/365,error= function(e) {0}))
  ## Effective age due to cancer
  effage.agesw <- effage0tiss * effage0 + effagert * (agesw - 20)
  survyrswf = sapply(effage.agesw,function(a) tryCatch(simdeath(r20wf,ageratewf,a,k)/365,error= function(e) {0}))
